Abstract Binding Trees

### 2015-10-22 paper.tex
restore sentence I accidentally deleted
Fix morphism part for Grothendieck construction

\newcommand\Grothendieck[2]{\oint^{#1} #2#1}
\newcommand\Pair[2]{\langle #1, #2 \rangle}

@@

Via the Grothendieck construction\footnote{Category of elements.}
$\Grothendieck{}{}$ on the operator presheaf $\Operators$ we also have a
category with objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\Member{\vartheta}{f^{*}\Operators}\Pair{\Upsilon'}{\varrho'} = \vartheta'$.

>>>>

\newcommand\Grothendieck[2]{\oint^{#1} #2#1}
\newcommand\Pair[2]{\langle #1, #2 \rangle}
\newcommand\Restriction[1]{#1^{*}}

@@

Then, fix a covariant presheaf of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{Category of elements.} $\Grothendieck{}{}$ on the operator
presheaf $\Operators$ we also have a category with objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\Member{\Restriction{f}\vartheta =
  \vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
